---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  collapse = TRUE
)
```

# nyclodging

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`nyclogding` contains shiny application and documentation for analyzing Airbnb listings in New York City in 2019. 


```{r}
nyclodging::listings
```


Shiny app:  https://qiushiyan.shinyapps.io/nyclodging/

Package documentation: https://qiushiyan.github.io/nyclodging


## Installation

You can install the development version of nyclodging like so:

``` r
remotes::install_github("qiushiyan/nyclodging")
```

## Usage

To start the shiny app locally

```{r usage, eval = FALSE}
library(nyclodging)
run_app()
```

Or if you prefer using docker 

```
docker pull qiushiyan/nyclodging
docker run -p 8080:80 --rm qiushiyan/nyclodging
```

and then navigate to http://localhost:8080/

## Source 

- Inside Airbnb public data http://insideairbnb.com/

- Kaggle Dataset https://www.kaggle.com/dgomonov/new-york-city-airbnb-open-data


